\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}

\begin{document}
\begin{center}
	{\Large \textsc{Physical Chemistry Lab II}}

	CHEM 3625
\end{center}

\begin{center}
	{\large Spring 2025}
\end{center}
\begin{center}
	\rule{0.99\textwidth}{0.4pt}
	\begin{tabular}{llcll}
		\textbf{Instructor:} & Matthew Rowley           &  & \textbf{Office Hours:} & Daily 10:00 am -- 11:00 am \\
		\textbf{Telephone:}  & (435) 586-7875           &  &                        &                            \\
		\textbf{Email:}      & matthewrowley$1$@suu.edu &  & \textbf{Office:}       & SC-220                     \\
		\multicolumn{5}{c}{Please include the course number in the subject line of all correspondence.}
	\end{tabular}
	\rule{0.99\textwidth}{0.4pt}
\end{center}

\section*{Tentative Schedule}
This class will meet on Thursdays from 3:30pm -- 5:20pm in room 224 of the Science Center (SC)

\paragraph{Week 1: Jan. 8 -- Jan. 10}~

No Lab

\paragraph{Week 2: Jan. 13 -- Jan. 17}~

Group 1: Quantum Dots and Particle in a Box – A Spectroscopic Study

Group 2: Vibrational-Rotational Spectra of HCl/DCl
\paragraph{Week 3: Jan. 20 -- Jan. 24}~

Group 3: Quantum Dots and Particle in a Box – A Spectroscopic Study

Group 4: Vibrational-Rotational Spectra of HCl/DCl
% Exp 1: Quantum Dots and Particle in a Box – A Spectroscopic Study

\paragraph{Week 4: Jan. 27 -- Jan. 31}~

Group 1: Vibrational-Rotational Spectra of HCl/DCl

Group 2: Quantum Dots and Particle in a Box – A Spectroscopic Study
% No Lab -- Analyze Quantum Dot Data
\paragraph{Week 5: Feb. 3 -- Feb. 7}~

Group 3: Vibrational-Rotational Spectra of HCl/DCl

Group 4: Quantum Dots and Particle in a Box – A Spectroscopic Study
% Exp. 2: Absorption Spectrum of Conjugated Dyes

\paragraph{Week 6: Feb. 10 -- Feb. 14}~

Group 1: Absorption Spectrum of Conjugated Dyes

Group 2: Computational Applications of Quantum Chemistry
% No Lab -- Analyze Conjugated Dyes Data

\paragraph{Week 7: Feb. 17 -- Feb. 21}~

Group 3: Absorption Spectrum of Conjugated Dyes

Group 4: Computational Applications of Quantum Chemistry
% Exp. 3: Photophysics of Pyrene

\paragraph{Week 8: Feb. 24 -- Feb. 28}~

Group 1: Computational Applications of Quantum Chemistry

Group 2: Absorption Spectrum of Conjugated Dyes
% No Lab -- Analyze Pyrene Data

\paragraph{Week 9: Mar. 3 -- Mar. 7}~

Group 3: Computational Applications of Quantum Chemistry

Group 4: Absorption Spectrum of Conjugated Dyes
% Exp 4: Computational Applications of Quantum Chemistry

\paragraph{Week 10: Mar. 10 -- Mar. 14}~

\textbf{No lab -- Spring Break!}

\paragraph{Week 11: Mar. 17 -- Mar. 21}~

Group 1: Photophysics of Pyrene

Group 2: Calculation of π-type Delocalized Orbitals Using Hückle Theory
% No Lab -- Analyze Computational Data

\paragraph{Week 12: Mar. 24 -- Mar. 28}~

Group 3: Photophysics of Pyrene

Group 4: Calculation of π-type Delocalized Orbitals Using Hückle Theory
% Exp. 5: Vibrational-Rotational Spectra of HCl/DCl

\paragraph{Week 13: Mar. 31 -- Apr. 4}~

Group 1: Calculation of π-type Delocalized Orbitals Using Hückle Theory

Group 2: Photophysics of Pyrene
% No Lab -- Analyze HCl/DCl Data

\paragraph{Week 14: Apr. 7 -- Apr. 11}~

Group 3: Calculation of π-type Delocalized Orbitals Using Hückle Theory

Group 4: Photophysics of Pyrene
% Exp. 6: Calculation of π-type Delocalized Orbitals Using Hückle Theory

\paragraph{Week 15: Apr. 14 -- Apr. 18}~

\textbf{Final Exam}

\paragraph{Finals Week}~

No Final -- You took it last week!

But don't forget the literature report!

\end{document}
